Appendix

### 2021-04-02 manuscript/appendix.Rmd
:broom:

---
title: 'Appendix'
date: "`r Sys.Date()`"
author: Carl Boettiger
journal: TBD
layout: 3p
bibliography: refs.bib
csl: csl/ecology-letters.csl
#output:
#  tufte::tufte_handout:
#    dev: cairo_pdf
#    latex_engine: xelatex
output: 
  hrbrthemes::ipsum_pdf:
    dev: cairo_pdf
    latex_engine: xelatex

>>>>

---
title: 'Appendix'
author: Carl Boettiger
journal: TBD
layout: 3p
bibliography: refs.bib
csl: csl/ecology-letters.csl
#output:
#  tufte::tufte_handout:
#    dev: cairo_pdf
#    latex_engine: xelatex
output: 
  hrbrthemes::ipsum_pdf:
    dev: cairo_pdf
    latex_engine: xelatex
